R Notebook

### 2019-08-14 analysis/final_analysis.Rmd
add analyses of chagne over ti e

>>>>

Examine how listeners might be adapting

```{r}
critTrials %>% 
  #filter(condition == 'scripted') %>%
  group_by(gameid) %>% 
  mutate(trialNum = row_number(),
         lastRoundIncorrect = 1-lag(correct)) %>% 
  group_by(trialNum) %>% 
  summarize(prop = sum(correct)/length(correct)) %>%
  mutate(error = ifelse(correct == 0, 'error', 'no error')) %>%
  ggplot(aes(x= trialNum, y = n, color = lastRoundIncorrect)) +
    geom_line()
```

```{r}
library(brms)
summary(brm(correct ~ trialNum + (1 + trialNum| gameid), family = 'bernoulli', 
              data = critTrials %>%   
                    group_by(gameid) %>%
                    mutate(trialNum = row_number(),
                           lastRoundIncorrect = 1-lag(correct)), control = list(adapt_delta = .95)))
```
